material and methods

### 2017-08-25 man/ms_1_material_methods.Rmd
update methods: standardized anomalies

:red_circle: reescribir esto de la calidad.

@@

>>>>

:red_circle: reescribir esto de la calidad. Ver Samanta et al 2012 y como describe el proceso de calidad

@@

To explore the effect of drought events on greenness we calculated the EVI standardized anomaly (EVI~sa) pixel-by-pixel, since it minimizes biases in the evaluation of anomalies, providing more information about the magnitude of the anomalies [@Samanta2012, @Gao2016]. For each pixel we averaged all the EVI valid values within a year (:red_filter: see quality filter), and then the standardized anomaly was computed as:

$$\mathrm{EVI_{sa,\mathit{i}}}= \frac{\mathrm{EVI_{mean,\mathit{i}}-EVI_{mean,ref}}}{\sigma_{\mathrm{ref}}}$$
where $\mathrm{EVI_{sa,\mathit{i}}}$ is the EVI standardized anomaly for the year $i$;  $\mathrm{EVI_{mean,\mathit{i}}}$ the annual mean value of EVI for the year $i$; $\mathrm{EVI_{mean,ref}}$ the average of the annual EVI values for the period of reference (all except $i$ year), and $\sigma_{\mathrm{ref}}$ the standard deviation for the reference period.
